Syntax-Based Concept Alignment for Domain-Specific Machine Translation

### 2021-05-09 paper/paper.tex
data section of eval

\section{Evaluation} \label{evaluation}
\subsection{Data}
% PUD treebanks
% plans (+UDPipe)
% langs

\subsection{Evaluating CE} % TODO: find better title?
\subsubsection{Experimental setup} % TODO: find better title?
% metrics & methods
\subsubsection{Results}
% PUD (incl. reason-wise?): independent, comparison with SMT
% RAW
\subsubsection{Discussion}

\subsection{MT experiments}
\subsubsection{Experimental setup}
\subsubsection{Results}
\subsubsection{Discussion}

>>>>

\section{Evaluation} \label{evaluation}
\subsection{Data}
Because we want part of our evaluation to be independent from the quality of UD parsing, some of the experiments are carried out using manually annotated data. 
To this purpose, we use a 100-sentences subset of the Parallel UD (PUD) corpus, a set of handcrafted\footnote{Annotation is sometimes semi-automatic, but all treebanks are at least manually checked.} multilingual treebanks in CoNLL-U format created for the CoNLL 2017 shared task on Multilingual Parsing from Raw Text to Universal Dependencies \cite{TODO:}.
PUD treebanks are available in over 20 languages, of which we selected English, Italian and Swedish. 
Using this data limits the amount of alignment errors that are due annotation issues to a minimum, even though a small number of inconsistencies and imprecisions is present even in this corpus.

When it comes to testing the program on raw text, we use two bilingual sentence-aligned corpora consisting of course plans from the Department of Mathematics and Computer Science of the University of Perugia (for English-Italian) and from the Department of Computer Science and Engineering (CSE) shared between the University of Gothenburg and the Chalmers University of Technology (for English-Swedish). For brevity, we will refer to these two datasets as to the DMI and the CSE corpora.
This data, available in the project repository, was collected and sentence-aligned specifically for this work and a related Bachelor's thesis project \cite{TODO:}.
When using raw text, our parser of choice is UDPipe \cite{TODO:}. 
In particular, we use the ParTUT English and Italian models for the DMI corpus and models trained on the bilingual LinES English-Swedish treebank for the CSE corpus \cite{TODO:}.

\subsection{Evaluating CE} % TODO: find better title?
% metrics & methods
\subsubsection{Results}
% PUD (incl. reason-wise?): independent, comparison with SMT
% RAW
\subsubsection{Discussion}

\subsection{MT experiments}
% metrics & methods
\subsubsection{Results}
\subsubsection{Discussion}
